Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2013-08-02 paper.tex
move hydro changes to the appendix

@@

>>>>

We use the unsplit PPM solver in Castro to advance the hydrodynamics
system in time.  A number of changes were made to the solver, which are 
detailed in the Appendix.  These changes bring the algorithm more in 
line with that of \cite{ppm}.

@@

\clearpage
\appendix

\section{Castro hydrodynamics changes}

Summary of changes:
\begin{itemize}
\item New reference state/flattening fix: helps energy conservation a
  lot, also fixes some undershoot/overshoots

\item New gravity update type: fixes some energy conservation

\item temperature-based PPM: fixes temperature floors

\item changing I's to use limit of the parabola instead of the
  cell-center: not sure if this does much

\item Colella \& Glaz Riemann solver: does a much better job with
  temperature in strong shocks

\item Tracing of gravity: seems to help with the material at the edge
  of the star
\end{itemize}
